---
title: "Plot.ly for p8105_hw4_co2554"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---
### Problem 2

Lets make some graphs using `plot.ly` and the `p8105.datasets` package:

```{r setup, message = FALSE}
library(tidyverse)
library(plotly)
library(viridis)

library(p8105.datasets)
```

I'll be using the `ny_noaa` dataset to create my graphs and flexdashboard. I'm curious to see what the weather was like in three different regions of New York in 2005.

First, let's clean up our data.
```{r nydat}
data("ny_noaa")

ny_noaa =
  ny_noaa |>
  mutate(name = recode(id, 
                      "USW00094728" = "Central_Park", 
                      "USW00014733" = "Buffalo",
                      "USC00308746" = "Tupper_Lake_Sunmount"), 
         tmin = as.numeric(tmin) / 10, 
         tmax = as.numeric(tmax) / 10, 
         prcp = (prcp) / 10) |>
  filter(
         year(date) == 2005,
         name %in% c("Central_Park", "Buffalo", "Tupper_Lake_Sunmount"),
         if_all(c(prcp, snow, snwd, tmax, tmin), ~!is.na(.))) |>
  select(name, date, prcp, snow, snwd, tmax, tmin)
```

Now, let's compare the distribution of temperature in Central Park (Manhattan), Buffalo, and Tupper Lake Sunmount using a density plot.

```{r density}
ny_noaa |>
  select(name, tmax, tmin) |> 
  pivot_longer(
    tmax:tmin,
    names_to = "observation",
    values_to = "temp") |> 
plot_ly(x = ~temp, color = ~name, colors = viridis(3), type = "histogram", histnorm = "probability density") |> 
  layout(
    xaxis = list(title = "Temperature (°C)"),
    yaxis = list(title = "Density"),
    title = "Distribution of Temperature (2005)",
    showlegend = TRUE
  )
```

Since Central Park runs a bit warmer than the two, I'm interested to see if there's more precipitation here.

```{r precipitation}
ny_noaa |> 
  select(name, prcp, snow) |> 
  plot_ly(x = ~name) |> 
  add_bars(y = ~prcp, name = "Rainfall", marker = list(color = ~viridisLite::viridis(2)[1])) |> 
  add_bars(y = ~snow, name = "Snowfall", marker = list(color = ~viridisLite::viridis(2)[2])) |> 
  layout(
    title = "Annual Precipitation (2005)",
    xaxis = list(
      title = "Location"),
    yaxis = list(title = "Amount (mm)"),
    barmode = "group"
  )
```

Buffalo gets a lot of snow, and I'm not surprised that Central Park has the largest annual rainfall. I wonder what the correlation is between `snow` and `snowd`. Let's make a scatter plot.


```{r scatter}
ny_noaa |>
  select(snow, snwd, name) |>
  plot_ly(x = ~snow, y = ~snwd, color = ~name, type = "scatter", mode = "markers", colors = "viridis" ) |>
  layout(
    title = "Snow vs. Snow Depth (2005)",
    xaxis = list(title = "Snowfall (mm)"),
    yaxis = list(title = "Snow Depth (mm)"),
    showlegend = TRUE)

```

