---
title: "Plot.ly for p8105_hw4_co2554"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
---
### Problem 2

Lets make some graphs using `plot.ly` and the `p8105.datasets` package:

```{r setup, message = FALSE}
library(tidyverse)
library(plotly)
library(viridis)

library(p8105.datasets)
```

I'll be using the `ny_noaa` dataset to create my graphs and flexdashboard. I'm curious to see what the weather was like in three different regions of New York the year I was born.

First, let's make a time series line plot of precipitation in Central Park (Manhattan), Buffalo, and in a smaller city, Tupper Lake Sunmount.

```{r nydat}
data("ny_noaa")

ny_noaa =
  ny_noaa |>
  mutate(name = recode(id, 
                      "USW00094728" = "Central_Park", 
                      "USW00014733" = "Buffalo",
                      "USC00308746" = "Tupper_Lake_Sunmount"), 
         tmin = as.numeric(tmin) / 10, 
         tmax = as.numeric(tmax) / 10) |>
  filter(year(date) == 1999,
         name %in% c("Central_Park", "Buffalo", "Tupper_Lake_Sunmount"),
         if_all(c(prcp, snow, snwd, tmax, tmin), ~!is.na(.))) |>
  select(name, date, prcp, snow, snwd, tmax, tmin)
```


Let's compare the distibution of temperature high's in Central Park, Buffalo, and Tupper Lake Sunmount using a density plot.
```{r density}
plot_ly(ny_noaa, x = ~tmax, color = ~name, colors = viridis(3), type = "histogram", histnorm = "probability density") |> 
  layout(
    xaxis = list(title = "Max Temperature (°C)"),
    yaxis = list(title = "Density"),
    title = "Density Distribution of Max Temp (tmax) in 1999",
    showlegend = TRUE
  )
```
  
In 1999, it appears that in Buffalo, Central Park, and Tupper Lake Summit, `tmax` is left-skewed, with the average peaks for all three being roughly between 20 - 25 celcius. It makes sense that Central Park has the most variation in max temperature and has higher `tmax` averages, since its the most southern-lying city we are comparing in the state. 

